---
title: "MPI_demo"
author: "Kittiya Kukiattikun"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MPI_demo}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
  
---

## Simple Simulation

```{r warning=F, message=F}
library(MPI)
library(kableExtra)
```

### Loading Data

`MPI::examplePovertydf` is a simulation poverty data frame contains 16 indicators column which 1 means failed and 0 means passed

And forth administrative regions of France in Region column

```{r}
data(examplePovertydf)
```
```{r example, results = 'asis', echo = FALSE}
kable(head(examplePovertydf, n = 3), 
      "html", 
      col.names = gsub("[.]", " ", names(examplePovertydf))) %>% 
  kable_styling()
```

### Calculation

For calculating MPI using `AF_Seq` (for sequential run) or `AF_Par` (for parallel run)
```{r}
out_seq <- AF_Seq(examplePovertydf, g = "Region", k = 3)
```

Output will be *list of lists* separated into group, and each list contains
* groupname 
* H (Uncensored head count) 
* A (Average deprivation share among row)
* M0 (Multidimensional Poverty Index) 
```{r, echo=FALSE}
out_seq[[1]]$groupname
out_seq[[1]]$H
out_seq[[1]]$A
out_seq[[1]]$M0
```
* DimentionalContribution (Dimensional contributions) 
```{r outt1, results = 'asis', echo=FALSE}
kable(out_seq[[1]]$DimentionalContribution, 
            "html",
            col.names = gsub("[.]", " ", names(out_seq[[1]]$DimentionalContribution))) %>%
  kable_styling()
```
* pov_df (poverty data frame) 
```{r outt2, results = 'asis', echo=FALSE}
kable(out_seq[[1]]$pov_df, 
            "html",
            col.names = gsub("[.]", " ", names(out_seq[[1]]$pov_df))) %>%
  kable_styling()
```
